Twists of supersymmetric gauge theories

### 2019-11-15 paper.tex
some susy action calculation in 6d

Using this decomposition, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.  We begin by considering $\mr O(8)$ itself.
\begin{prop} \label{O8_decomposition_of_susy_prop}

After reduction to $\mr O(8)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^-)\rangle + \langle \phi_1,^\vee (Q^+,\lambda^+)\rangle + \langle \lambda^{+\vee}, \sd F_A Q_+ \rangle + \langle \lambda^{-\vee}, \rho(\dd \phi_1)Q_+ \rangle\\
I^{(2)}(Q^+, Q^+) &= (\lambda^{+\vee}, \lambda^{+\vee})(Q^+,Q^+) + (\lambda^{+\vee},Q^+)^2 + \langle c^\vee, \phi_1\rangle(Q_+,Q_+)
\end{align*}
if $Q^+$ is an element of $S_+$, and
\begin{align*}
I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^+)\rangle + \langle \wt \phi_1^\vee, (Q^-,\lambda^-)\rangle+ \langle \lambda^{-\vee}, \sd F_A Q_- \rangle + \langle \lambda^{+\vee}, \rho(\dd \wt \phi_1)Q_- \rangle\\
I^{(2)}(Q^-, Q^-) &= (\lambda^{-\vee}, \lambda^{-\vee})(Q^-,Q^-) + (\lambda^{-\vee},Q^-)^2 + \langle c^\vee, \wt \phi_1\rangle(Q_-,Q_-)
\end{align*}
if $Q^-$ is an element of $S_-$.
\end{prop}

@@

\subsection{Dimension 6}

% \cN=(1, 1) SYM, three twists identical to dimension 8

% \cN=(1, 0) SYM with matter in a pseudo-real representation, one twist.

\subsubsection{$\cN=(1,0)$ with hypermultiplet matter}

>>>>

Using this decomposition, we can describe the supersymmetric interaction terms $I^{(1)}$ and $I^{(2)}$ after reduction from 10d to 8d, with respect to various subgroups of $\mr O(8)$.  We begin by considering $\mr O(8)$ itself.

\begin{prop} \label{O8_decomposition_of_susy_prop}
After reduction to $\mr O(8)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^-)\rangle + \langle \phi_1,^\vee (Q^+,\lambda^+)\rangle + \langle \lambda^{+\vee}, \sd F_A Q_+ \rangle + \langle \lambda^{-\vee}, \rho(\dd \phi_1)Q_+ \rangle\\
I^{(2)}(Q^+, Q^+) &= (\lambda^{+\vee}, \lambda^{+\vee})(Q^+,Q^+) + (\lambda^{+\vee},Q^+)^2 + \langle c^\vee, \phi_1\rangle(Q_+,Q_+)
\end{align*}
if $Q^+$ is an element of $S_+$, and
\begin{align*}
I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^+)\rangle + \langle \wt \phi_1^\vee, (Q^-,\lambda^-)\rangle+ \langle \lambda^{-\vee}, \sd F_A Q_- \rangle + \langle \lambda^{+\vee}, \rho(\dd \wt \phi_1)Q_- \rangle\\
I^{(2)}(Q^-, Q^-) &= (\lambda^{-\vee}, \lambda^{-\vee})(Q^-,Q^-) + (\lambda^{-\vee},Q^-)^2 + \langle c^\vee, \wt \phi_1\rangle(Q_-,Q_-)
\end{align*}
if $Q^-$ is an element of $S_-$.
\end{prop}

@@

\subsection{Dimension 6}
In dimension 6 there are two possible supersymmetry groups by which we can act.  There is a minimal supersymmetric field theory with $\mc N=(1,0)$ supersymmetry, consisting of a pure gauge theory coupled to matter living in a symplectic representation $V$.  If $V \iso T^*\gg$, then the $(1,0)$ supersymmetry can be enhanced to $\mc N=(1,1)$ supersymmetry.  This is the theory one obtains by compactifying 10d $\mc N=1$ super Yang-Mills down to $\RR^6$.

\subsubsection{$\mc N = (1,0)$ with hypermultiplet matter}

\subsubsection{$\mc N = (1,1)$ Super Yang-Mills Theory}

Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills on $\RR^6$ as $c$, the ghost, along with:
\begin{itemize}
 \item Bosons: a gauge field $A$, along with 4 scalars $\{\phi_i\}$.  These transform in the vector representation of the R-symmetry group $\Spin(4)_R$, i.e. the tensor product $W_+ \otimes W_-$ of the two fundamental representations of $\Sp(W_+) \times \Sp(W_-)$.  We'll write just $\phi$ for the scalars, viewed as a section of the trivial $W_+ \otimes W_-$-bundle on $\RR^6$.
 \item Fermions: spinor fields $\psi^+ \otimes u^+$ and $\psi^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
\end{itemize}

\begin{prop} \label{O6_decomposition_of_susy_prop}
After reduction to $\mr O(6)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^+)\rangle\omega(w^+,u^+) + \langle \phi^\vee, (Q^+,\lambda^-)\rangle w^+ \otimes u^- + \\&\qquad + \langle (\lambda^{+} \otimes u^+)^\vee, \sd F_A (Q^+ \otimes w^+) \rangle + \langle (\lambda^{-} \otimes u^-)^\vee, \rho(\dd \phi)(Q^+ \otimes w^+) \rangle\\
I^{(2)}(Q^+, Q^+) &= \left(\langle\lambda^{+\vee},Q^+\rangle\langle u^{+\vee}, w^+ \rangle\right)^2
\end{align*}
if $Q^+ \otimes w^+$ is an element of $S_+ \otimes W_+$, and
\begin{align*}
I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^-)\rangle\omega(w^-,u^-) + \langle \phi^\vee, (Q^-,\lambda^+)\rangle w^- \otimes u^+ + \\&\qquad + \langle (\lambda^{-} \otimes u^-)^\vee, \sd F_A (Q^- \otimes w^-) \rangle + \langle (\lambda^{+} \otimes u^+)^\vee, \rho(\dd \phi)(Q^- \otimes w^-) \rangle\\
I^{(2)}(Q^-, Q^-) &= \left(\langle\lambda^{-\vee},Q^-\rangle\langle u^{-\vee}, w^- \rangle\right)^2
\end{align*}
if $Q^- \otimes W_-$ is an element of $S_- \otimes W_-$.  In each of these expressions, we have suppressed in the notation some contractions of tensors between $W_+ \otimes W_-$ and its dual.  There is an additional term in $I^{(2)}$ associated to the action of a rank $(1,1)$ supercharge $Q^+ + Q^-$, which takes the form
\[I^{(2)}(Q^+, Q^-) = (\lambda^{+\vee}, \lambda^{-\vee})(Q^+,Q^-) \langle, u^{+\vee} \otimes u^{-\vee}, w^+ \otimes w^-\rangle + \langle c^\vee, \phi \rangle(Q^+,Q^-) w^+ \otimes w^-. \]
\end{prop}

\begin{remark}
If we set $\lambda^- \otimes u^-$ and $\phi$ to zero, and consider only the action of $Q^+ \otimes w^+$, then we recover the supersymmetry action for the $\mc N=(1,0)$ pure gauge theory.  If instead we set $\lambda^+ \otimes u^+$ and $A$ to zero, and consider only the action of $Q^- \otimes w^-$ then we recover the supersymmetry action for the $\mc N=(1,0)$ pure matter theory.
\end{remark}
